\vspace{-5mm}Equation-free analysis of a dynamically evolving multigraph

### 2016-02-03 report/multigraph_manuscript.tex
Finalized illustrations of transients and, to a lesser extent, cpi
The following produces reasonable results with the current pref_attach
executable:

mpirun -n 100 ./pref_attach -n 100 -m 50000 -s 2000000
-project -offManifoldWait 10000 -nMicroSteps 60000 -save_interval 10000
-collectionInterval 1000 -kappa 1 -projStep 30000

Deg-seq error between this and

mpirun -n 100 ./pref_attach -n 100 -m 50000 -s 2000000
-project -offManifoldWait 10000 -nMicroSteps 60000 -save_interval 10000
-collectionInterval 1000 -kappa 1 -projStep 30000 -noinit

is low, but the coefficients hardly align, probably d

\begin{figure}[ht!]
  % TODO
  \centering
  \includegraphics[width=0.5\textwidth]{placeholder}
  \caption{Figure showing evolution of some property (probably triangle distribution) over time, starting from two different initial conditions. Here we're illustrating that unimportant, higher-order variables quickly fall onto the same point on the slow manifold despite different starting at different values. \label{fig:sv}}
\end{figure}

@@

>>>>

\begin{figure}[ht!]
  % TODO
  \centering
  \includegraphics[width=0.5\textwidth]{triangle-slaving}
  \caption{Figure showing evolution of triangle counts over time,
    starting from three different initial networks that shared the
    same degree sequence. Thus higher-order variables that may be
    initialized off the slow manifold are quickly drawn to it
    ($O(n^2)$ steps). \label{fig:sv}}
\end{figure}

@@

\begin{figure}[ht!]
  % TODO
  \centering
  \includegraphics[width=0.75\textwidth]{pca-2d-rho-kappa}
  \caption{Embedding of steady states in $\rho$ / $\kappa$ plane,
    showing that PCA can uncover the two-dimensional structure of the
    dataset. \label{fig:pca}}
\end{figure}
